Advantages of mixed unitary operators for quantum information processing

### 2018-12-08 decorrelation/mixed_unitaries.tex
a few more changes to the experimental section

% ==============================================================================
% Section: Experimental Results
% ==============================================================================
\section{Experimental Results}
\label{sec:experimental_results}
Here we present experimental results from implementing our routine on a fixed-frequency superconducting transmon qubit. In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}. To implement a MUP on this qubit, four incorrectly calibrated approximately Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.

Using the COBYLA minimizer in \texttt{scipy.optimize}\cite{scipy} to perform constrained minimization of the off--diagonal elements of the produced channel. This is a form of Sequential Quadratic Programming\cite{wright1999numerical}. \note{Explain why this an okay thing to do, or reference the section where we explain it.} To benchmark the quality of the new MUP, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process. We used $1000$ shots per experiment, $10$ sequences per sequence length, for sequence lengths of $2, 4, 8, 16, 32$ and $64$. In each case, our Clifford operations were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses. In our implementation, these gates are implemented using the same pulse envelope definitions and control electronics, phase shifted by $\frac{\pi}{2}$ radians, and are therefore subject to identical miscalibration errors. The results are shown in Figure \ref{fig:rb} for sequence lengths $L=64$. The complete dataset can be found at  \cite{decorrelating_errors}.

>>>>

% ==============================================================================
% Section: Experimental Results
% ==============================================================================
\section{Experimental Results}
\label{sec:experimental_results}
Here we present experimental results from implementing our routine on a fixed-frequency superconducting transmon qubit. In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}. To implement a MUP on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.

Using the COBYLA minimizer in \texttt{scipy.optimize}\cite{scipy} to perform constrained minimization via Sequential Quadratic Programming\cite{wright1999numerical}, we minimized the off--diagonal elements of the resulting mixed process. \note{Explain why this an okay thing to do, or reference the section where we explain it.} To benchmark the quality of the new MUP, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process. We used $1000$ shots per experiment, $10$ sequences per sequence length, for sequence lengths of $2, 4, 8, 16, 32$ and $64$. In each case, our Clifford operations were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses. In our implementation, these gates are implemented using the same pulse envelope definitions and control electronics, phase shifted by $\frac{\pi}{2}$ radians, and are therefore subject to identical miscalibration errors. The results are shown in Figure \ref{fig:rb} for sequence lengths $L=64$. The complete dataset can be found at  \cite{decorrelating_errors}.
